QRF Covariate Selection

### 2020-02-05 analysis/R_scripts/fit_qrf_model.Rmd
traded riparian cover: understory for riparian cover: big trees in the QRF model. Re-ran whole script.

```{r habitat-covariates}
sel_hab_mets = tibble(Species = c('Chinook'),
                      Metric = c("WetWDRat_Avg",
                                 "CU_Freq",
                                 "DpthWet_SD",
                                 "WetBraid",
                                 "FishCovTotal",
                                 "RipCovUstory",
                                 'WetWdth_Int',
                                 'Q',
                                 "SubLT6",
                                 "SubD16",
                                 "avg_aug_temp",
                                 "LWFreq_Wet"))
                      # 
                      # Metric = c('UcutArea_Pct',
                      #            'FishCovNone',
                      #            'SubEstGrvl',
                      #            'FstTurb_Freq',
                      #            'FstNT_Freq',
                      #            'CU_Freq',
                      #            'SlowWater_Pct',
                      #            'NatPrin1',
                      #            'DistPrin1',
                      #            'avg_aug_temp',
                      #            # 'Sin_CL',
                      #            'Sin',
                      #            'WetWdth_CV',
                      #            'WetBraid',
                      #            'WetSC_Pct',
                      #            'Q',
                      #            'WetWdth_Int',
                      #            'LWFreq_Wet',
                      #            'LWVol_WetFstTurb'))

>>>>

```{r habitat-covariates}
sel_hab_mets = tibble(Species = c('Chinook'),
                      Metric = c("WetWDRat_Avg",
                                 "CU_Freq",
                                 "DpthWet_SD",
                                 "WetBraid",
                                 "FishCovTotal",
                                 # "RipCovUstory",
                                 "RipCovBigTree",
                                 'WetWdth_Int',
                                 'Q',
                                 "SubLT6",
                                 "SubD16",
                                 "avg_aug_temp",
                                 "LWFreq_Wet"))
                      # 
                      # Metric = c('UcutArea_Pct',
                      #            'FishCovNone',
                      #            'SubEstGrvl',
                      #            'FstTurb_Freq',
                      #            'FstNT_Freq',
                      #            'CU_Freq',
                      #            'SlowWater_Pct',
                      #            'NatPrin1',
                      #            'DistPrin1',
                      #            'avg_aug_temp',
                      #            # 'Sin_CL',
                      #            'Sin',
                      #            'WetWdth_CV',
                      #            'WetBraid',
                      #            'WetSC_Pct',
                      #            'Q',
                      #            'WetWdth_Int',
                      #            'LWFreq_Wet',
                      #            'LWVol_WetFstTurb'))
